Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering

### 2014-09-12 evaluation.tex
Fix up citations.

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 1.7-7x with an average of 4x with null metadata filtering.
This is an average reduction in overheads of 65\%. For BC, normalized execution
times drop from 16x down to FIXMEx on average (an FIXME\% reduction). The range of normalized execution
times for filtered BC is FIXME-FIXMEx. This is not surprising since in the baseline
implementation all loads and stores needed to be monitored. However, with
filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 10\% overheads
on average after filtering, an 88\% reduction in monitoring overheads, with a
maximum overhead of 31\% after filtering. This is due, in part, to the fact
that
for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would expect to see less filtering. IMP does not have
null metadata and thus is not affected by null metadata filtering.

>>>>

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 1.7-7x with an average of 4x with null metadata filtering.
This is an average reduction in overheads of 65\%. For BC, normalized execution
times drop from 16x down to 3x on average (an 80\% reduction). The range of normalized execution
times for filtered BC is 1.1-8.3x. This is not surprising since in the baseline
implementation all loads and stores needed to be monitored. However, with
filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 10\% overheads
on average after filtering, an 88\% reduction in monitoring overheads, with a
maximum overhead of 31\% after filtering. This is due, in part, to the fact
that
for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would expect to see less filtering. IMP does not have
null metadata and thus is not affected by null metadata filtering.

### 2014-09-12 monitoring.tex
Fix up citations.

There have been a number of proposals for run-time monitoring systems exploring various
design points. % in the trade-off space between efficiency and flexibility.
Table~\ref{tab:monitoring.previous_overheads} summarizes some of representative designs
and their reported performance overhead. The previous studies clearly show that there
exist trade-offs among efficiency, flexibility, and hardware costs. 
For example, a run-time monitoring scheme can often be realized with fairly low
performance overhead (less than 20\%) if implemented with custom hardware that is
designed only for one monitor or a narrow set of monitors. However, the custom
hardware monitors cannot be modified or updated, and require dedicated silicon area. 
On the other hand, flexible systems that support a wide range of monitors lead 
to noticeable performance overhead, often too high for wide deployment in practice.
Software-only implementations \cite{FIXME} or multi-core monitors with minimal
hardware changes \cite{lba-asid06} are reported to have severalfold slowdowns.
On-chip FPGA monitors \cite{flexcore-micro10} and cores with monitoring accelerators
\cite{lba-isca08, fade-hpca14} can reduce overhead significantly, but still show
slowdowns of several tens of percents in some cases.
In today's monitoring systems, the overhead is also unpredictable because they
depend heavily on the characteristics of applications and monitoring operations.
In summary, users currently need to either pay noticeable overhead or the cost of custom
hardware in order to use fine-grained run-time monitoring in deployed systems.

@@

{\bf Cooperative testing, debugging, and protection:}
Recently studies \cite{FIXME} have shown that software testing, debugging,
or attack detection may be done in a cooperative fashion across
a large number of systems. In this case, each system is only willing to pay very low
overhead, say a few percents, and only performs a small subset of checks. 
A high coverage is achieved by having different systems check different parts of a program.
The partial monitoring framework allows high-overhead monitoring to be used in a
cooperative fashion. 
The main metric that represents the effectiveness of monitoring in this case is
the coverage (the percentage of checks there were performed) over multiple runs.

@@

{\bf Profiling:} 
The run-time monitoring system can be used to implement various profiling tools
to collect statistics on program behaviors for performance optimizations as well
as security protection. For example, a recent study showed that an instruction
mix can be used to identify malware from normal programs \cite{FIXME}. 
In such profiling tools, the partial monitoring framework can be used to obtain
the statics on samples rather than all program events, essentially trading off
accuracy for lower overhead.

>>>>

There have been a number of proposals for run-time monitoring systems exploring various
design points. % in the trade-off space between efficiency and flexibility.
Table~\ref{tab:monitoring.previous_overheads} summarizes some of representative designs
and their reported performance overhead. The previous studies clearly show that there
exist trade-offs among efficiency, flexibility, and hardware costs. 
For example, a run-time monitoring scheme can often be realized with fairly low
performance overhead (less than 20\%) if implemented with custom hardware that is
designed only for one monitor or a narrow set of monitors. However, the custom
hardware monitors cannot be modified or updated, and require dedicated silicon area. 
On the other hand, flexible systems that support a wide range of monitors lead 
to noticeable performance overhead, often too high for wide deployment in practice.
Software-only implementations \cite{nagarajan-interact08, lift-micro06,
purify-usenix92, taintcheck-ndsss05} or multi-core monitors with minimal
hardware changes \cite{lba-asid06} are reported to have severalfold slowdowns.
On-chip FPGA monitors \cite{flexcore-micro10} and cores with monitoring accelerators
\cite{lba-isca08, fade-hpca14} can reduce overhead significantly, but still show
slowdowns of several tens of percents in some cases.
In today's monitoring systems, the overhead is also unpredictable because they
depend heavily on the characteristics of applications and monitoring operations.
In summary, users currently need to either pay noticeable overhead or the cost of custom
hardware in order to use fine-grained run-time monitoring in deployed systems.

@@

{\bf Cooperative testing, debugging, and protection:}
Recently studies \cite{liblit-pldi05, chilimbi-asplos04, greathouse-cgo11, testudo-micro08} have shown that software testing, debugging,
or attack detection may be done in a cooperative fashion across
a large number of systems. In this case, each system is only willing to pay very low
overhead, say a few percents, and only performs a small subset of checks. 
A high coverage is achieved by having different systems check different parts of a program.
The partial monitoring framework allows high-overhead monitoring to be used in a
cooperative fashion. 
The main metric that represents the effectiveness of monitoring in this case is
the coverage (the percentage of checks there were performed) over multiple runs.

@@

{\bf Profiling:} 
The run-time monitoring system can be used to implement various profiling tools
to collect statistics on program behaviors for performance optimizations as well
as security protection. For example, a recent study showed that an instruction
mix can be used to identify malware from normal programs \cite{demme-isca13, tang-raid14}. 
In such profiling tools, the partial monitoring framework can be used to obtain
the statics on samples rather than all program events, essentially trading off
accuracy for lower overhead.

### 2014-09-12 tabs/previous_overheads.tex
Fix up citations.

FlexCore \cite{flexcore-micro10} & Dedicated FPGA & Instruction-trace monitoring & 1.05x-1.44x / 1.84x \\ \hline
FADE \cite{FIXME} & Core+Custom HW & Instruction-trace monitoring (effective when HW filters work) & \\ \hline
LBA-accelerated \cite{lba-isca08} & Multi-core+Custom HW & Instruction-trace monitoring (effective when accelerators work) & 1.02x-3.27x / 5x \\ \hline
LBA \cite{lba-asid06} & Multi-core+Custom HW & Instruction trace monitoring & 3.23x-7.80x / 11x \\ \hline \hline

@@

LIFT \cite{lift-micro06} & SW (DBI) & DIFT (fully flexible) & 3.6x / 7.9x \\ \hline
Purfiy \cite{purify-usenix92} & SW (DBI) & Memory leak checks (fully flexible) & 2.3x / 5.5x \\ \hline
TaintCheck \cite{taintcheck-05} & SW (DBI) & DIFT (fully flexible) & 10x / 27x \\ \hline

>>>>

FlexCore \cite{flexcore-micro10} & Dedicated FPGA & Instruction-trace monitoring & 1.05x-1.44x / 1.84x \\ \hline
FADE \cite{fade-hpca14} & Core+Custom HW & Instruction-trace monitoring (effective when HW filters work) & 1.2x-1.8x / 3.3x \\ \hline
LBA-accelerated \cite{lba-isca08} & Multi-core+Custom HW & Instruction-trace monitoring (effective when accelerators work) & 1.02x-3.27x / 5x \\ \hline
LBA \cite{lba-asid06} & Multi-core+Custom HW & Instruction trace monitoring & 3.23x-7.80x / 11x \\ \hline \hline

@@

LIFT \cite{lift-micro06} & SW (DBI) & DIFT (fully flexible) & 3.6x / 7.9x \\ \hline
Purfiy \cite{purify-usenix92} & SW (DBI) & Memory leak checks (fully flexible) & 2.3x / 5.5x \\ \hline
TaintCheck \cite{taintcheck-ndsss05} & SW (DBI) & DIFT (fully flexible) & 10x / 27x \\ \hline
